\onlyinsubfile{\setcounter{section}{3}}
\section{Results}\notinsubfile{\label{sec:results}}

%\setcounter{page}{0}\pagenumbering{arabic}
\subsection{Determinants of trust}

\par First, I go beyond correlations between the variables by trying to consider which variables explain the variation in the trust measures.

\input{../../Code/Regressions/Trust/trust_reg_general.tex}  

\subsection{Income and trust}

\par After understanding the determinants of trust in the HRS data, I wanted to see if the \say{hump-shape} relationship between trust and income found by \cite{jbpglg2016} was present in the HRS data. To do this I used the available income data from the 2020 wave with the trust measures from the same year.

\par First, I consider the statistical relationship for labor income in the following figures. 

\input{../../Code/Regressions/Income/Labor/income_trust_general_log.tex}

\input{../../Code/Regressions/Income/Labor/income_trust_general_ihs.tex}

\par The pattern seems to be stronger for total income, based on the figure .

\input{../../Code/Regressions/Income/Total/income_trust_general_log.tex}

\input{../../Code/Regressions/Income/Total/income_trust_general_ihs.tex}

\subsection{Returns and trust}

\par With the hump-shape relationship between earnings and trust present in the HRS, I wanted to see if a similar relationship held for returns.

\par The smallest portfolio composition is of core assets only. The regression results for raw and winsorized annual returns for 2022 are given in figures and .

\input{../../Code/Regressions/Returns/Core/returns_r1_trust_general_win.tex}
\FloatBarrier

\input{../../Code/Regressions/Returns/Core/returns_r1_trust_general.tex}
\FloatBarrier

\par The next portfolio composition includes retirement assets along with those core assets. The regression results for raw and winsorized annual returns for 2022 on these portfolios are given in figures and .

\input{../../Code/Regressions/Returns/Core+res/returns_r4_trust_general_win.tex}
\FloatBarrier

\input{../../Code/Regressions/Returns/Core+res/returns_r4_trust_general.tex}
\FloatBarrier


\par The largest portfolio composition is on net wealth, which includes the previous assets, residential assets, along with other smaller categories (and debt variables). The regression results for raw and winsorized annual returns to net wealth for 2022 are given in figures and .

\input{../../Code/Regressions/Returns/Net wealth/returns_r5_trust_general_win.tex}
\FloatBarrier

\input{../../Code/Regressions/Returns/Net wealth/returns_r5_trust_general.tex}
\FloatBarrier


\subsection{Returns from 2002-2022}

\par Next, I wanted to compute returns across several years and attempt to describe the persistent component of returns that \cite{aflgdmlp20} point to as heterogeneity across individuals. I also use three similar specifications. First, a pooled OLS regression with a baseline set of controls. Second, a similar pooled regression with aimed at controlling for risk exposure. Third, a panel regression with individual fixed effects and year dummies.

\section{The pooled regression with constant trust}

\par After looking at those specifications for the returns regressions, I wanted to see if the trust measure was significant in the pooled setting. 

\subsection{Trust and average income}

\subsection{Trust and average returns}

\subsection{Estimated fixed effects for returns}